Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-06-01 mu/article/article.tex
Writing introduction.

\blindtext
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/upstruc2}
    \\
    \includegraphics[width=\linewidth]{figures/upstruc1}
    \caption{Up structure}
    \label{fig:up-struc}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/altstruc2}
    \\
    \includegraphics[width=\linewidth]{figures/altstruc1}
    \caption{Alt structure.}
    \label{fig:alt-struc}
\end{figure}
\blindtext
\blindtext

\blindtext

@@

0.2\,eV (top panel)  which include the THz and the Mid Infrared (MIR) radiation,
where the absolute maximum of the

@@

angles but for an energy range between 1.90\,eV and 2.05\,eV.
In the top frames of top and bottom panels of Fig. \ref{fig:up-vaz-rag} we
present in solid lines the result of evaluate
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$, related to the left scale,
fixing the energy of the incoming beam to 0.088\,eV and 1.972\,eV, respectively,
values for which the response is maximized for the \emph{up} structure. In the
same panels and frames we present in dashed lines, related to the right scale,
the corresponding velocity angle $\gamma_{\mathrm{z}}(\omega,\alpha)$, and in
the bottom frames of the panels we present the corresponding components
$\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$ and
$\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Also we present two circled and

@@

to $\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 65.5^{\circ}$ and resulting in
a value of the response of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
82.3$\,Km/s indicated by the upward green arrow.

@@

Now, from bottom panels of Figs. \ref{fig:up-3d-vsz} and \ref{fig:up-vaz-rag} we
have that the most intense local maximum of the response is obtained for an

@@

$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=30.3$\,Km/s. This comes from
a major contribution of the $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$ component
being directed in a velocity angle $\gamma_{\mathrm{z}}(\omega,\alpha) =
78^{\circ}$ on the first Cartesian Quadrant on the $xy$ plane.

@@

that the velocity angle is almost constant at $78^{\circ}$ and has variations of
$1^{\circ}$ for polarization angles $0^{\circ} \leq \alpha \leq 100^{\circ}$. In
this range the green circled box indicates the value for which the polarization
angle and the response direction angle are collinear corresponding to
$\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 78.5^{\circ}$ and having a
response value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| =
23.5$\,Km/s indicated with the green upward arrow.

@@

In Fig. \ref{fig:alt-3d-vsb} we analyzed the energy range for the incident beam
from 0.6\,eV to 1.0\,eV, corresponding to the NIR radiation, where the absolute
maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is
obtained for the \emph{alt} structure .
% From this figure we found that the zone where the absolute maximum response is
% held corresponds to a energy range from 0.90\,eV to 0.93\,eV and polarization
% angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a local maximum
% is obtained for the same polarization angles but for energies between 0.67\,eV
% and 0.75\,eV.
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
% 
{\color{red} From Figs. \ref{fig:alt-3d-vsb} and \ref{fig:alt-vaz-rag} we have
that the absolute maximum response is obtained for an incoming beam with
polarization angle $\alpha=145^{\circ}$ reaching a velocity of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 43.0$\,Km/s for the spin
polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)=50^{\circ}$ on the first Cartesian Quadrant
of the $xy$ plane.
% 
Also, from the top frame of Fig. \ref{fig:alt-vaz-rag} we found that the
velocity angle is centered at $51.5^{\circ}$ having variations of $\pm
2^{\circ}$ for the polarization angle range $0^{\circ} \leq
\alpha \leq 180^{\circ}$.
% 
As made in the previous analysis the circled box indicates the collinear angle
(Eq. \eqref{eq:gamma-par}) $\gamma_{\mathrm{z}\parallel}(\omega,\alpha) =
53.5^{\circ}$ corresponding a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 12.7$\,Km/s; the blue
square box indicates the perpendicular angles corresponding values
$\alpha=140^{\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha)=50^{\circ}$
with a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43$\,Km/s.}
% 
Again, for the cases in which the spin polarization is parallel to the surface
of the \emph{alt} structure was calculated but the plots are not presented here.
The absolute maxima for the cases when the spin polarization are directed in the
$\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of the
incoming beam equal to 0.912\,eV and polarization angle $\alpha=145^{\circ}$
resulting in values of
$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=27.1$\,Km/s and
$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)|=33.2$\,Km/s.

@@

$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ for this structure. To this absolute
maximum corresponds spin polarization polar and azimuthal angles

@@

almost perpendicularly over the $xy$ plane and  localized on the first Cartesian
quadrant.}

@@

for the $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ only the polar angle is held
at $8^{\circ}$ for the peak of the response having variations of $\pm 2^{\circ}$
but the azimuthal angle changes from $99^{\circ}$ to $176^{\circ}$ having a
value of $133^{\circ}$ for the maximum.

@@

{\color{red} We found that for both cases the components have similar contributions for each
response and for 1.934\,eV result in values of

@@

moving along the $x$ direction with polar and azimuthal spin polarization angles
$\theta_{\mathrm{x}}(\omega,\alpha)= 42^{\circ}$ and

@@

intense local maxima for which all the components have similar contributions for
both responses.

@@

This result in values of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)| = 9.9$\,Km/s
and $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| = 49.4$\,Km/s with spin
polarization angles $\theta_{\mathrm{x}}(\omega,\alpha) = 129^{\circ}$,

@@

downward the third Cartesian quadrant of the $xy$ plane when it moves in the $x$
direction and downward the third Cartesian quadrant when it moves along the $y$
direction.}

@@

polarization and current changes the direction. After an energy of 2.05\,eV both
responses goes to zero.

>>>>

\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/upstruc2}
    \\
    \includegraphics[width=\linewidth]{figures/upstruc1}
    \caption{Up structure}
    \label{fig:up-struc}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{figures/altstruc2}
    \\
    \includegraphics[width=\linewidth]{figures/altstruc1}
    \caption{Alt structure.}
    \label{fig:alt-struc}
\end{figure}

Since its discovery, graphene has attracted a great interest in materials
science and condensed matter physics being a new class of materials that are
only one atom thick\cite{geimNM07}. This allotrope of carbon with hexagonal
lattice structure is almost transparent and presents properties like fractional
quantum Hall effect at room temperature, excellent thermal transport
properties, high conductivity and strength \cite{geimNM07, reinaNL08,
novoselov2S07, balandinNL08} and is a perfect platform to be used in two-
dimensions electronic systems; however most electronic applications are
disabled by the absence of a semiconducting gap. Recent studies demonstrate
that the band gap of graphene can be opened by applying an electric
field\cite{zhangN09}, reducing the surface area\cite{hanPRL07} or applying
uniaxial strain\cite{niACSN08}. Another option to open the gap is by doping;
this has been successfully achieved using boron and nitrogen\cite{guoIJ11} and
hydrogen\cite{eliasS09, guisingerNL09, samarakoonACSN10}.

Hydrogenated graphene can result in different structures depending of the
percentage of hydrogenation and the position at which they are bonded in the
hexagonal lattice. In this paper we present a study made on two 50\%
hydrogenated graphene structures, \emph{up} and \emph{alt} , both showing a
opening of the gap. As shown in Figs. \ref{fig:up-struc} and 
\ref{fig:alt-struc} the \emph{up} structure has hydrogen atoms bonded to the
carbon layer only in the upper side of the structure while the \emph{alt}
structure has hydrogen alternating in the upper and bottom sides of the carbon
slab.

We conduct a theoretical study of the spin velocity injection, being this a
nonlinear response, in both structures. We analyze particularly the cases when
the spin is polarized along a Cartesian direction or when the velocity is
directed along the $x$ or $y$ directions on the $xy$ plane of the structures.

@@

0.2\,eV (top panel)  which include the THz and the Mid Infrared (MIR)
radiation, where the absolute maximum of the

@@

angles but for an energy range between 1.90\,eV and 2.05\,eV. In the top frames
of top and bottom panels of Fig. \ref{fig:up-vaz-rag} we present in solid lines
the result of evaluate $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$,
related to the left scale, fixing the energy of the incoming beam to 0.088\,eV
and 1.972\,eV, respectively, values for which the response is maximized for the
\emph{up} structure. In the same panels and frames we present in dashed lines,
related to the right scale, the corresponding velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)$, and in the bottom frames of the panels we
present the corresponding components $\mathcal{V}^{\mathrm{xz}}(\omega,\alpha)$
and $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$. Also we present two circled and

@@

to $\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 65.5^{\circ}$ and resulting
in a value of the response of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 82.3$\,Km/s indicated by
the upward green arrow.

@@

Now, from bottom panels of Figs. \ref{fig:up-3d-vsz} and \ref{fig:up-vaz-rag}
we have that the most intense local maximum of the response is obtained for an

@@

$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=30.3$\,Km/s. This comes
from a major contribution of the $\mathcal{V}^{\mathrm{yz}}(\omega,\alpha)$
component being directed in a velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha) = 78^{\circ}$ on the first Cartesian
Quadrant on the $xy$ plane.

@@

that the velocity angle is almost constant at $78^{\circ}$ and has variations
of $1^{\circ}$ for polarization angles $0^{\circ} \leq \alpha \leq
100^{\circ}$. In this range the green circled box indicates the value for which
the polarization angle and the response direction angle are collinear
corresponding to $\gamma_{\mathrm{z}\parallel}(\omega,\alpha) = 78.5^{\circ}$
and having a response value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 23.5$\,Km/s indicated
with the green upward arrow.

@@

In Fig. \ref{fig:alt-3d-vsb} we analyzed the energy range for the incident beam
from 0.6\,eV to 1.0\,eV, corresponding to the NIR radiation, where the absolute
maximum of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|$ response is
obtained for the \emph{alt} structure .
% From this figure we found that the zone where the absolute maximum response
% is held corresponds to a energy range from 0.90\,eV to 0.93\,eV and
% polarization angles $\alpha$ between $120^{\circ}$ and $150^{\circ}$. Also, a
% local maximum is obtained for the same polarization angles but for energies
% between 0.67\,eV and 0.75\,eV.
% %%%%%%%%%%%%%%%%%
% %% 0.0 eV - 0.16 eV
% %% Description of ALT |V_{s^z}| & gamma  vs. alpha agle
% %%%%%%%%%%%%%%%%%
% 
{\color{red} From Figs. \ref{fig:alt-3d-vsb} and \ref{fig:alt-vaz-rag} we have
that the absolute maximum response is obtained for an incoming beam with
polarization angle $\alpha=145^{\circ}$ reaching a velocity of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 43.0$\,Km/s for the spin
polarized in the $\mathrm{z}$ direction and resulting in a velocity angle
$\gamma_{\mathrm{z}}(\omega,\alpha)=50^{\circ}$ on the first Cartesian Quadrant
of the $xy$ plane.
% 
Also, from the top frame of Fig. \ref{fig:alt-vaz-rag} we found that the
velocity angle is centered at $51.5^{\circ}$ having variations of $\pm
2^{\circ}$ for the polarization angle range $0^{\circ} \leq
\alpha \leq 180^{\circ}$.
% 
As made in the previous analysis the circled box indicates the collinear angle
(Eq. \eqref{eq:gamma-par}) $\gamma_{\mathrm{z}\parallel}(\omega,\alpha) =
53.5^{\circ}$ corresponding a value of
$|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)| = 12.7$\,Km/s; the blue
square box indicates the perpendicular angles corresponding values
$\alpha=140^{\circ}$ and $\gamma_{\mathrm{z}\perp}(\omega,\alpha)=50^{\circ}$
with a value of $|\mathcal{V}_{\sigma^{\mathrm{z}}}(\omega,\alpha)|=43$\,Km/s.}
% 
Again, for the cases in which the spin polarization is parallel to the surface
of the \emph{alt} structure was calculated but the plots are not presented
here. The absolute maxima for the cases when the spin polarization are directed
in the $\mathrm{x}$ and $\mathrm{y}$ direction are obtained for an energy of
the incoming beam equal to 0.912\,eV and polarization angle
$\alpha=145^{\circ}$ resulting in values of
$|\mathcal{V}_{\sigma^{\mathrm{x}}}(\omega,\alpha)|=27.1$\,Km/s and
$|\mathcal{V}_{\sigma^{\mathrm{y}}}(\omega,\alpha)|=33.2$\,Km/s.

@@

$|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)|$ for this structure. To this
absolute maximum corresponds spin polarization polar and azimuthal angles

@@

almost perpendicularly over the $xy$ plane and  localized on the first
Cartesian quadrant.}

@@

for the $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)|$ only the polar angle is
held at $8^{\circ}$ for the peak of the response having variations of $\pm
2^{\circ}$ but the azimuthal angle changes from $99^{\circ}$ to $176^{\circ}$
having a value of $133^{\circ}$ for the maximum.

@@

{\color{red} We found that for both cases the components have similar
contributions for each response and for 1.934\,eV result in values of

@@

moving along the $x$ direction with polar and azimuthal spin polarization
angles $\theta_{\mathrm{x}}(\omega,\alpha)= 42^{\circ}$ and

@@

intense local maxima for which all the components have similar contributions
for both responses.

@@

This result in values of $|\mathcal{V}^{\mathrm{x}}(\omega,\alpha)| =
9.9$\,Km/s and $|\mathcal{V}^{\mathrm{y}}(\omega,\alpha)| = 49.4$\,Km/s with
spin polarization angles $\theta_{\mathrm{x}}(\omega,\alpha) = 129^{\circ}$,

@@

downward the third Cartesian quadrant of the $xy$ plane when it moves in the
$x$ direction and downward the third Cartesian quadrant when it moves along the
$y$ direction.}

@@

polarization and current changes the direction. After an energy of 2.05\,eV
both responses goes to zero.
